---
title: "Semantic Plots"
author: "Jeff Brabec"
date: "10/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(janitor)
library(safejoin)
library(gprofiler2)
library(yardstick)
library(viridis)
library(readxl)
library(patchwork)
library(writexl)
library(ggrepel)
source(here("src/get_scrnaseq_data.R"))
source(here("src/semantic_plot.R"))
source(here("src/get_ont.R"))
```

# No Pathology v. All Pathology

## Read in scRNAseq Data
In the markdown document `process_deg_data` we extracted the DEG for each cell type and merged together the gene lists of like cell types (neuron and glia) into pan-cell type gene lists. The abbreviations `np_ap` designate No-pathology v. Any Pathology. Both early and Late pathology groups are included in "any pathology".
```{r}
#Excitatory Neuron Data
ex_neu_np_ap_degs <- read_rds(here("data/single_cell_data/no_path_v_all_path/ex_neu_np_ap_degs.rds"))

#Inhibitory Neuron Data
in_neu_np_ap_degs <- read_rds(here("data/single_cell_data/no_path_v_all_path/in_neu_np_ap_degs.rds"))

#Astrocyte Data
ast_np_ap_degs <- read_rds(here("data/single_cell_data/no_path_v_all_path/ast_np_ap_degs.rds"))

#Microglia Data
micro_np_ap_degs <- read_rds(here("data/single_cell_data/no_path_v_all_path/micro_np_ap_degs.rds"))

#Oligodendrocyte Data
olig_np_ap_degs <- read_rds(here("data/single_cell_data/no_path_v_all_path/olig_np_ap_degs.rds"))

#Oligodendrocyte Precursor Cell Data
opc_np_ap_degs <- read_rds(here("data/single_cell_data/no_path_v_all_path/opc_np_ap_degs.rds"))

#Pan-Neuronal Data
pan_neuron_np_ap_degs <- read_rds(here("data/single_cell_data/no_path_v_all_path/pan_neuron_np_ap_degs.rds"))

#Pan-Glial Data
pan_glia_np_ap_degs <- read_rds(here("data/single_cell_data/no_path_v_all_path/pan_glia_np_ap_degs.rds"))
```

## Ontology

### Excitatory Neuron
```{r}
en_np_ap_ont <- map(ex_neu_np_ap_degs, get_ont, organism = "hsapiens")
write_xlsx(en_np_ap_ont, here("results/rnaseq_ontology/gost_res/no_path_v_all_path/en_ont.xlsx"))

en_np_ap_up_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_all_path/en_neu_up_revigo.csv"), 
                                      title = "Excitatory Neuron Up-Regulated Ontology", 
                                      subtitle = "No Pathology V. All Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_all_path/en_np_ap_up_sem_plot.png"),
       en_np_ap_up_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
en_np_ap_down_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_all_path/ex_neu_down_revigo.csv"), 
                                        title = "Excitatory Neuron Down-Regulated Ontology", 
                                        subtitle = "No Pathology V. All Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_all_path/en_np_ap_down_sem_plot.png"),
       en_np_ap_down_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
en_np_ap_all_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_all_path/ex_neu_all_revigo.csv"),
                                       title = "Excitatory Neuron All DEG Ontology",
                                       subtitle = "No Pathology V. All Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_all_path/en_np_ap_all_sem_plot.png"),
       en_np_ap_all_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)

```

### Inhibitory Neuron
Nothing much of interest so moved on
```{r}

in_np_ap_ont <- map(in_neu_np_ap_degs, get_ont, organism = "hsapiens", significant = FALSE)
write_xlsx(in_np_ap_ont, here("results/rnaseq_ontology/gost_res/no_path_v_all_path/in_ont.xlsx"))

```

### Astrocyte

```{r}
ast_np_ap_ont <- map(ast_np_ap_degs, get_ont, organism = "hsapiens", significant = FALSE)
write_xlsx(ast_np_ap_ont, here("results/rnaseq_ontology/gost_res/no_path_v_all_path/ast_ont.xlsx"))

ast_np_ap_up_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_all_path/ast_up_revigo.csv"), 
                                       title = "Astrocyte Up-Regulated Ontology", 
                                       subtitle = "No Pathology V. All Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_all_path/ast_np_ap_up_sem_plot.png"),
       ast_np_ap_up_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
```

### Microglia

```{r}
micro_np_ap_ont <- map(micro_np_ap_degs, get_ont, organism = "hsapiens", significant = FALSE)
write_xlsx(micro_np_ap_ont, here("results/rnaseq_ontology/gost_res/no_path_v_all_path/micro_ont.xlsx"))

micro_np_ap_up_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_all_path/micro_up_revigo.csv"), 
                                         title = "Microglia Up-Regulated Ontology", 
                                         subtitle = "No Pathology V. All Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_all_path/micro_np_ap_up_sem_plot.png"),
       micro_np_ap_up_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
micro_np_ap_all_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_all_path/micro_all_revigo.csv"), 
                                          title = "Microglia All DEG Ontology", 
                                          subtitle = "No Pathology V. All Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_all_path/micro_np_ap_all_sem_plot.png"),
       micro_np_ap_all_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
```

### Oligodendrocyte

```{r}
olig_np_ap_ont <- map(olig_np_ap_degs, get_ont, organism = "hsapiens")
write_xlsx(olig_np_ap_ont, here("results/rnaseq_ontology/gost_res/no_path_v_all_path/olig_ont.xlsx"))

olig_np_ap_up_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_all_path/olig_up_revigo.csv"), 
                                         title = "Oligodendrocyte Up-Regulated Ontology", 
                                         subtitle = "No Pathology V. All Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_all_path/olig_np_ap_up_sem_plot.png"),
       olig_np_ap_up_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
olig_np_ap_down_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_all_path/olig_down_revigo.csv"), 
                                         title = "Oligodendrocyte Down-Regulated Ontology", 
                                         subtitle = "No Pathology V. All Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_all_path/olig_np_ap_down_sem_plot.png"),
       olig_np_ap_down_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
olig_np_ap_all_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_all_path/olig_all_revigo.csv"), 
                                          title = "Oligodendrocyte All DEG Ontology", 
                                          subtitle = "No Pathology V. All Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_all_path/olig_np_ap_all_sem_plot.png"),
       olig_np_ap_all_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
```

### OPC
```{r}
opc_np_ap_ont <- map(opc_np_ap_degs, get_ont, organism = "hsapiens", significant = FALSE)
write_xlsx(opc_np_ap_ont, here("results/rnaseq_ontology/gost_res/no_path_v_all_path/opc_ont.xlsx"))
#None Significant

# opc_np_ap_up_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_all_path/opc_up_revigo.csv"), 
#                                          title = "OPC Up-Regulated Ontology", 
#                                          subtitle = "No Pathology V. All Pathology")
# ggsave(here("results/figures/semantic_plots/no_path_v_all_path/opc_np_ap_up_sem_plot.png"),
#        opc_np_ap_up_sem_plot,
#        height = 8,
#        width = 8,
#        units = "in",
#        dpi = 600)
# opc_np_ap_down_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_all_path/opc_down_revigo.csv"), 
#                                          title = "OPC Down-Regulated Ontology", 
#                                          subtitle = "No Pathology V. All Pathology")
# ggsave(here("results/figures/semantic_plots/no_path_v_all_path/opc_np_ap_down_sem_plot.png"),
#        opc_np_ap_down_sem_plot,
#        height = 8,
#        width = 8,
#        units = "in",
#        dpi = 600)
# opc_np_ap_all_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_all_path/opc_all_revigo.csv"), 
#                                           title = "OPC All DEG Ontology", 
#                                           subtitle = "No Pathology V. All Pathology")
# ggsave(here("results/figures/semantic_plots/no_path_v_all_path/opc_np_ap_all_sem_plot.png"),
#        opc_np_ap_all_sem_plot,
#        height = 8,
#        width = 8,
#        units = "in",
#        dpi = 600)
```

### Pan-Neuronal
```{r}
pan_neuron_np_ap_ont <- map(pan_neuron_np_ap_degs, get_ont, organism = "hsapiens")
write_xlsx(pan_neuron_np_ap_ont, here("results/rnaseq_ontology/gost_res/no_path_v_all_path/pan_neuron_ont.xlsx"))

pan_neuron_np_ap_up_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_all_path/pan_neuron_up_revigo.csv"),
                                         title = "Pan-Neuronal Up-Regulated Ontology",
                                         subtitle = "No Pathology V. All Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_all_path/pan_neuron_np_ap_up_sem_plot.png"),
       pan_neuron_np_ap_up_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
pan_neuron_np_ap_down_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_all_path/pan_neuron_down_revigo.csv"),
                                         title = "Pan-Neuronal Down-Regulated Ontology",
                                         subtitle = "No Pathology V. All Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_all_path/pan_neuron_np_ap_down_sem_plot.png"),
       pan_neuron_np_ap_down_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
pan_neuron_np_ap_all_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_all_path/pan_neuron_all_revigo.csv"),
                                          title = "Pan-Neuronal All DEG Ontology",
                                          subtitle = "No Pathology V. All Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_all_path/pan_neuron_np_ap_all_sem_plot.png"),
       pan_neuron_np_ap_all_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
```

### Pan-Glial

```{r}
pan_glia_np_ap_ont <- map(pan_glia_np_ap_degs, get_ont, organism = "hsapiens", significant = FALSE)
write_xlsx(pan_glia_np_ap_ont, here("results/rnaseq_ontology/gost_res/no_path_v_all_path/pan_glia_ont.xlsx"))

pan_glia_np_ap_up_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_all_path/pan_glia_up_revigo.csv"),
                                         title = "Pan-Glial Up-Regulated Ontology",
                                         subtitle = "No Pathology V. All Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_all_path/pan_glia_np_ap_up_sem_plot.png"),
       pan_glia_np_ap_up_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
pan_glia_np_ap_all_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_all_path/pan_glia_all_revigo.csv"),
                                          title = "Pan-Glial All DEG Ontology",
                                          subtitle = "No Pathology V. All Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_all_path/pan_glia_np_ap_all_sem_plot.png"),
       pan_glia_np_ap_all_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
```


# No Pathology V. Early Pathology

## Read in scRNAseq Data
Here we use the custom function `get_scrnaseq_data` which reads in a specified section of the excel sheet and splits that data into UP, DOWN, and ALL genes based on Z score. 
## Read in scRNAseq Data
In the markdown document `process_deg_data` we extracted the DEG for each cell type and merged together the gene lists of like cell types (neuron and glia) into pan-cell type gene lists. 
```{r}
#Excitatory Neuron Data
ex_neu_np_ep_degs <- read_rds(here("data/single_cell_data/no_path_v_early_path/ex_neu_np_ep_degs.rds"))

#Inhibitory Neuron Data
in_neu_np_ep_degs <- read_rds(here("data/single_cell_data/no_path_v_early_path/in_neu_np_ep_degs.rds"))

#Astrocyte Data
ast_np_ep_degs <- read_rds(here("data/single_cell_data/no_path_v_early_path/ast_np_ep_degs.rds"))

#Microglia Data
micro_np_ep_degs <- read_rds(here("data/single_cell_data/no_path_v_early_path/micro_np_ep_degs.rds"))

#Oligodendrocyte Data
olig_np_ep_degs <- read_rds(here("data/single_cell_data/no_path_v_early_path/olig_np_ep_degs.rds"))

#Oligodendrocyte Precursor Cell Data
opc_np_ep_degs <- read_rds(here("data/single_cell_data/no_path_v_early_path/opc_np_ep_degs.rds"))

#Pan-Neuronal Data
pan_neuron_np_ep_degs <- read_rds(here("data/single_cell_data/no_path_v_early_path/pan_neuron_np_ep_degs.rds"))

#Pan-Glial Data
pan_glia_np_ep_degs <- read_rds(here("data/single_cell_data/no_path_v_early_path/pan_glia_np_ep_degs.rds"))
```

## Ontology

### Excitatory Neuron
```{r}
en_np_ep_ont <- map(ex_neu_np_ep_degs, get_ont, organism = "hsapiens")
write_xlsx(en_np_ep_ont, here("results/rnaseq_ontology/gost_res/no_path_v_early_path/en_ont.xlsx"))

en_np_ep_up_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_early_path/en_up_revigo.csv"), 
                                      title = "Excitatory Neuron Up-Regulated Ontology", 
                                      subtitle = "No Pathology V. Early Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_early_path/en_np_ep_up_sem_plot.png"),
       en_np_ep_up_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
en_np_ep_down_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_early_path/en_down_revigo.csv"), 
                                        title = "Excitatory Neuron Down-Regulated Ontology", 
                                        subtitle = "No Pathology V. Early Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_early_path/en_np_ep_down_sem_plot.png"),
       en_np_ep_down_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
en_np_ep_all_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_early_path/en_all_revigo.csv"),
                                       title = "Excitatory Neuron All DEG Ontology",
                                       subtitle = "No Pathology V. Early Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_early_path/en_np_ep_all_sem_plot.png"),
       en_np_ep_all_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)

```

### Inhibitory Neuron
Nothing much of interest so moved on
```{r}
in_np_ep_ont <- map(in_neu_np_ep_degs, get_ont, organism = "hsapiens", significant = FALSE)
write_xlsx(in_np_ep_ont, here("results/rnaseq_ontology/gost_res/no_path_v_early_path/in_ont.xlsx"))
#Up non-significant results
in_np_ep_down_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_early_path/in_down_revigo.csv"), 
                                        title = "Inhibitory Neuron Down-Regulated Ontology", 
                                        subtitle = "No Pathology V. Early Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_early_path/in_np_ep_down_sem_plot.png"),
       in_np_ep_down_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
in_np_ep_all_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_early_path/in_all_revigo.csv"),
                                       title = "Inhibitory Neuron All DEG Ontology",
                                       subtitle = "No Pathology V. Early Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_early_path/in_np_ep_all_sem_plot.png"),
       in_np_ep_all_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)

```

### Astrocyte

```{r}
ast_np_ep_ont <- map(ast_np_ep_degs, get_ont, organism = "hsapiens", significant = FALSE)
write_xlsx(ast_np_ep_ont, here("results/rnaseq_ontology/gost_res/no_path_v_early_path/ast_ont.xlsx"))
#Down non-significant results
#All not enough results

ast_np_ep_up_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_early_path/ast_up_revigo.csv"), 
                                       title = "Astrocyte Up-Regulated Ontology", 
                                       subtitle = "No Pathology V. Early Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_early_path/ast_np_ep_up_sem_plot.png"),
       ast_np_ep_up_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
```

### Microglia

```{r}
micro_np_ep_ont <- map(micro_np_ep_degs, get_ont, organism = "hsapiens")
write_xlsx(micro_np_ep_ont, here("results/rnaseq_ontology/gost_res/no_path_v_early_path/micro_ont.xlsx"))

micro_np_ep_up_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_early_path/micro_up_revigo.csv"), 
                                         title = "Microglia Up-Regulated Ontology", 
                                         subtitle = "No Pathology V. Early Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_early_path/micro_np_ep_up_sem_plot.png"),
       micro_np_ep_up_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
micro_np_ep_down_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_early_path/micro_down_revigo.csv"), 
                                         title = "Microglia Down-Regulated Ontology", 
                                         subtitle = "No Pathology V. Early Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_early_path/micro_np_ep_down_sem_plot.png"),
       micro_np_ep_down_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
micro_np_ep_all_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_early_path/micro_all_revigo.csv"), 
                                          title = "Microglia All DEG Ontology", 
                                          subtitle = "No Pathology V. Early Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_early_path/micro_np_ep_all_sem_plot.png"),
       micro_np_ep_all_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
```

### Oligodendrocyte
```{r}
olig_np_ep_ont <- map(olig_np_ep_degs, get_ont, organism = "hsapiens", significant = FALSE)
write_xlsx(olig_np_ep_ont, here("results/rnaseq_ontology/gost_res/no_path_v_early_path/olig_ont.xlsx"))

olig_np_ep_down_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_early_path/olig_down_revigo.csv"), 
                                         title = "Oligodendrocyte Down-Regulated Ontology", 
                                         subtitle = "No Pathology V. Early Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_early_path/olig_np_ep_down_sem_plot.png"),
       olig_np_ep_down_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
olig_np_ep_all_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_early_path/olig_all_revigo.csv"), 
                                          title = "Oligodendrocyte All DEG Ontology", 
                                          subtitle = "No Pathology V. Early Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_early_path/olig_np_ep_all_sem_plot.png"),
       olig_np_ep_all_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
```

### OPC
```{r}
opc_np_ep_ont <- map(opc_np_ep_degs, get_ont, organism = "hsapiens", significant = FALSE)
write_xlsx(opc_np_ep_ont, here("results/rnaseq_ontology/gost_res/no_path_v_early_path/opc_ont.xlsx"))

opc_np_ep_up_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_early_path/opc_up_revigo.csv"), 
                                         title = "OPC Up-Regulated Ontology", 
                                         subtitle = "No Pathology V. Early Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_early_path/opc_np_ep_up_sem_plot.png"),
       opc_np_ep_up_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)

```

### Pan-Neuronal
```{r}
pan_neuron_np_ep_ont <- map(pan_neuron_np_ep_degs, get_ont, organism = "hsapiens")
write_xlsx(pan_neuron_np_ep_ont, here("results/rnaseq_ontology/gost_res/no_path_v_early_path/pan_neuron_ont.xlsx"))

pan_neuron_np_ep_up_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_early_path/pan_neuron_up_revigo.csv"),
                                         title = "Pan-Neuronal Up-Regulated Ontology",
                                         subtitle = "No Pathology V. Early Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_early_path/pan_neuron_np_ep_up_sem_plot.png"),
       pan_neuron_np_ep_up_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
pan_neuron_np_ep_down_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_early_path/pan_neuron_down_revigo.csv"),
                                         title = "Pan-Neuronal Down-Regulated Ontology",
                                         subtitle = "No Pathology V. Early Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_early_path/pan_neuron_np_ep_down_sem_plot.png"),
       pan_neuron_np_ep_down_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
pan_neuron_np_ep_all_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_early_path/pan_neuron_all_revigo.csv"),
                                          title = "Pan-Neuronal All DEG Ontology",
                                          subtitle = "No Pathology V. Early Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_early_path/pan_neuron_np_ep_all_sem_plot.png"),
       pan_neuron_np_ep_all_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
```

### Pan-Glial
```{r}
pan_glia_np_ep_ont <- map(pan_glia_np_ep_degs, get_ont, organism = "hsapiens")
write_xlsx(pan_glia_np_ep_ont, here("results/rnaseq_ontology/gost_res/no_path_v_early_path/pan_glia_ont.xlsx"))

pan_glia_np_ep_up_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_early_path/pan_glia_up_revigo.csv"),
                                         title = "Pan-Glial Up-Regulated Ontology",
                                         subtitle = "No Pathology V. Early Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_early_path/pan_glia_np_ep_up_sem_plot.png"),
       pan_glia_np_ep_up_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
pan_glia_np_ep_down_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_early_path/pan_glia_down_revigo.csv"),
                                         title = "Pan-Glial Down-Regulated Ontology",
                                         subtitle = "No Pathology V. Early Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_early_path/pan_glia_np_ep_down_sem_plot.png"),
       pan_glia_np_ep_down_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
pan_glia_np_ep_all_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/no_path_v_early_path/pan_glia_all_revigo.csv"),
                                          title = "Pan-Glial All DEG Ontology",
                                          subtitle = "No Pathology V. Early Pathology")
ggsave(here("results/figures/semantic_plots/no_path_v_early_path/pan_glia_np_ep_all_sem_plot.png"),
       pan_glia_np_ep_all_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
```

# Early Pathology V. Late Pathology

## Read in scRNAseq Data
Here we use the custom function `get_scrnaseq_data` which reads in a specified section of the excel sheet and splits that data into UP, DOWN, and ALL genes based on Z score. Where `ep_lp` denotes early versus late pathology comparison.
```{r}
#Excitatory Neuron Data
ex_neu_ep_lp_degs <- read_rds(here("data/single_cell_data/early_path_v_late_path/ex_neu_ep_lp_degs.rds"))

#Inhibitory Neuron Data
in_neu_ep_lp_degs <- read_rds(here("data/single_cell_data/early_path_v_late_path/in_neu_ep_lp_degs.rds"))

#Astrocyte Data
ast_ep_lp_degs <- read_rds(here("data/single_cell_data/early_path_v_late_path/ast_ep_lp_degs.rds"))

#Microglia Data
micro_ep_lp_degs <- read_rds(here("data/single_cell_data/early_path_v_late_path/micro_ep_lp_degs.rds"))

#Oligodendrocyte Data
olig_ep_lp_degs <- read_rds(here("data/single_cell_data/early_path_v_late_path/olig_ep_lp_degs.rds"))

#Oligodendrocyte Precursor Cell Data
opc_ep_lp_degs <- read_rds(here("data/single_cell_data/early_path_v_late_path/opc_ep_lp_degs.rds"))

#Pan-Neuronal Data
pan_neuron_ep_lp_degs <- read_rds(here("data/single_cell_data/early_path_v_late_path/pan_neuron_ep_lp_degs.rds"))

#Pan-Glial Data
pan_glia_ep_lp_degs <- read_rds(here("data/single_cell_data/early_path_v_late_path/pan_glia_ep_lp_degs.rds"))
```

## Ontology

### Excitatory Neuron
```{r}
en_ep_lp_ont <- map(ex_neu_ep_lp_degs, get_ont, organism = "hsapiens")
write_xlsx(en_ep_lp_ont, here("results/rnaseq_ontology/gost_res/early_path_v_late_path/en_ont.xlsx"))

en_ep_lp_up_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/early_path_v_late_path/en_up_revigo.csv"), 
                                      title = "Excitatory Neuron Up-Regulated Ontology", 
                                      subtitle = "Early Pathology V. Late Pathology")
ggsave(here("results/figures/semantic_plots/early_path_v_late_path/en_ep_lp_up_sem_plot.png"),
       en_ep_lp_up_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
en_ep_lp_down_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/early_path_v_late_path/en_down_revigo.csv"), 
                                        title = "Excitatory Neuron Down-Regulated Ontology", 
                                        subtitle = "Early Pathology V. Late Pathology")
ggsave(here("results/figures/semantic_plots/early_path_v_late_path/en_ep_lp_down_sem_plot.png"),
       en_ep_lp_down_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
en_ep_lp_all_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/early_path_v_late_path/en_all_revigo.csv"),
                                       title = "Excitatory Neuron All DEG Ontology",
                                       subtitle = "Early Pathology V. Late Pathology")
ggsave(here("results/figures/semantic_plots/early_path_v_late_path/en_ep_lp_all_sem_plot.png"),
       en_ep_lp_all_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)

```

### Inhibitory Neuron
earlything much of interest so moved on
```{r}
in_ep_lp_ont <- map(in_neu_ep_lp_degs, get_ont, organism = "hsapiens")
write_xlsx(in_ep_lp_ont, here("results/rnaseq_ontology/gost_res/early_path_v_late_path/in_ont.xlsx"))

in_ep_lp_up_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/early_path_v_late_path/in_up_revigo.csv"), 
                                      title = "Excitatory Neuron Up-Regulated Ontology", 
                                      subtitle = "Early Pathology V. Late Pathology")
ggsave(here("results/figures/semantic_plots/early_path_v_late_path/in_ep_lp_up_sem_plot.png"),
       in_ep_lp_up_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
in_ep_lp_down_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/early_path_v_late_path/in_down_revigo.csv"), 
                                        title = "Inhibitory Neuron Down-Regulated Ontology", 
                                        subtitle = "Early Pathology V. Late Pathology")
ggsave(here("results/figures/semantic_plots/early_path_v_late_path/in_ep_lp_down_sem_plot.png"),
       in_ep_lp_down_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
in_ep_lp_all_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/early_path_v_late_path/in_all_revigo.csv"),
                                       title = "Inhibitory Neuron All DEG Ontology",
                                       subtitle = "Early Pathology V. Late Pathology")
ggsave(here("results/figures/semantic_plots/early_path_v_late_path/in_ep_lp_all_sem_plot.png"),
       in_ep_lp_all_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)

```

### Astrocyte

```{r}
ast_ep_lp_ont <- map(ast_ep_lp_degs, get_ont, organism = "hsapiens")
write_xlsx(ast_ep_lp_ont, here("results/rnaseq_ontology/gost_res/early_path_v_late_path/ast_ont.xlsx"))
#Down earlyn-significant results
#All earlyt eearlyugh results

ast_ep_lp_up_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/early_path_v_late_path/ast_up_revigo.csv"), 
                                       title = "Astrocyte Up-Regulated Ontology", 
                                       subtitle = "Early Pathology V. Late Pathology")
ggsave(here("results/figures/semantic_plots/early_path_v_late_path/ast_ep_lp_up_sem_plot.png"),
       ast_ep_lp_up_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
ast_ep_lp_down_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/early_path_v_late_path/ast_down_revigo.csv"), 
                                        title = "Astrocyte Down-Regulated Ontology", 
                                        subtitle = "Early Pathology V. Late Pathology")
ggsave(here("results/figures/semantic_plots/early_path_v_late_path/ast_ep_lp_down_sem_plot.png"),
       ast_ep_lp_down_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
ast_ep_lp_all_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/early_path_v_late_path/ast_all_revigo.csv"),
                                       title = "Astrocyte All DEG Ontology",
                                       subtitle = "Early Pathology V. Late Pathology")
ggsave(here("results/figures/semantic_plots/early_path_v_late_path/ast_ep_lp_all_sem_plot.png"),
       ast_ep_lp_all_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
```

### Microglia

```{r}
#not enough significant genes...
micro_ep_lp_ont <- map(micro_ep_lp_degs, get_ont, organism = "hsapiens")

```

### Oligodendrocyte
```{r}
olig_ep_lp_ont <- map(olig_ep_lp_degs, get_ont, organism = "hsapiens", significant = FALSE)
write_xlsx(olig_ep_lp_ont, here("results/rnaseq_ontology/gost_res/early_path_v_late_path/olig_ont.xlsx"))
#Down earlyn-significant results
#All earlyt eearlyugh results

olig_ep_lp_up_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/early_path_v_late_path/olig_up_revigo.csv"), 
                                       title = "Oligodendrocyte Up-Regulated Ontology", 
                                       subtitle = "Early Pathology V. Late Pathology")
ggsave(here("results/figures/semantic_plots/early_path_v_late_path/olig_ep_lp_up_sem_plot.png"),
       olig_ep_lp_up_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
olig_ep_lp_all_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/early_path_v_late_path/olig_all_revigo.csv"),
                                       title = "Oligodendrocyte All DEG Ontology",
                                       subtitle = "Early Pathology V. Late Pathology")
ggsave(here("results/figures/semantic_plots/early_path_v_late_path/olig_ep_lp_all_sem_plot.png"),
       olig_ep_lp_all_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
```

### OPC
```{r}
opc_ep_lp_ont <- map(opc_ep_lp_degs, get_ont, organism = "hsapiens", significant = FALSE)
write_xlsx(opc_ep_lp_ont, here("results/rnaseq_ontology/gost_res/early_path_v_late_path/opc_ont.xlsx"))
#Down earlyn-significant results
#All earlyt eearlyugh results

opc_ep_lp_up_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/early_path_v_late_path/opc_up_revigo.csv"), 
                                       title = "OPC Up-Regulated Ontology", 
                                       subtitle = "Early Pathology V. Late Pathology")
ggsave(here("results/figures/semantic_plots/early_path_v_late_path/opc_ep_lp_up_sem_plot.png"),
       opc_ep_lp_up_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
opc_ep_lp_all_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/early_path_v_late_path/opc_all_revigo.csv"),
                                       title = "OPC All DEG Ontology",
                                       subtitle = "Early Pathology V. Late Pathology")
ggsave(here("results/figures/semantic_plots/early_path_v_late_path/opc_ep_lp_all_sem_plot.png"),
       opc_ep_lp_all_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
```

### Pan-Neuronal
```{r}
pan_neuron_ep_lp_ont <- map(pan_neuron_ep_lp_degs, get_ont, organism = "hsapiens")
write_xlsx(pan_neuron_ep_lp_ont, here("results/rnaseq_ontology/gost_res/early_path_v_late_path/pan_neuron_ont.xlsx"))

pan_neuron_ep_lp_up_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/early_path_v_late_path/pan_neuron_up_revigo.csv"),
                                         title = "Pan-Neuronal Up-Regulated Ontology",
                                         subtitle = "Early Pathology V. Late Pathology")
ggsave(here("results/figures/semantic_plots/early_path_v_late_path/pan_neuron_ep_lp_up_sem_plot.png"),
       pan_neuron_ep_lp_up_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
pan_neuron_ep_lp_down_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/early_path_v_late_path/pan_neuron_down_revigo.csv"),
                                         title = "Pan-Neuronal Down-Regulated Ontology",
                                         subtitle = "Early Pathology V. Late Pathology")
ggsave(here("results/figures/semantic_plots/early_path_v_late_path/pan_neuron_ep_lp_down_sem_plot.png"),
       pan_neuron_ep_lp_down_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
pan_neuron_ep_lp_all_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/early_path_v_late_path/pan_neuron_all_revigo.csv"),
                                          title = "Pan-Neuronal All DEG Ontology",
                                          subtitle = "Early Pathology V. Late Pathology")
ggsave(here("results/figures/semantic_plots/early_path_v_late_path/pan_neuron_ep_lp_all_sem_plot.png"),
       pan_neuron_ep_lp_all_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
```

### Pan-Glial
```{r}
pan_glia_ep_lp_ont <- map(pan_glia_ep_lp_degs, get_ont, organism = "hsapiens")
write_xlsx(pan_glia_ep_lp_ont, here("results/rnaseq_ontology/gost_res/early_path_v_late_path/pan_glia_ont.xlsx"))

pan_glia_ep_lp_up_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/early_path_v_late_path/pan_glia_up_revigo.csv"),
                                         title = "Pan-Glial Up-Regulated Ontology",
                                         subtitle = "Early Pathology V. Late Pathology")
ggsave(here("results/figures/semantic_plots/early_path_v_late_path/pan_glia_ep_lp_up_sem_plot.png"),
       pan_glia_ep_lp_up_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
pan_glia_ep_lp_down_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/early_path_v_late_path/pan_glia_down_revigo.csv"),
                                         title = "Pan-Glial Down-Regulated Ontology",
                                         subtitle = "Early Pathology V. Late Pathology")
ggsave(here("results/figures/semantic_plots/early_path_v_late_path/pan_glia_ep_lp_down_sem_plot.png"),
       pan_glia_ep_lp_down_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
pan_glia_ep_lp_all_sem_plot <- semantic_plot(here("results/rnaseq_ontology/revigo_res/early_path_v_late_path/pan_glia_all_revigo.csv"),
                                          title = "Pan-Glial All DEG Ontology",
                                          subtitle = "Early Pathology V. Late Pathology")
ggsave(here("results/figures/semantic_plots/early_path_v_late_path/pan_glia_ep_lp_all_sem_plot.png"),
       pan_glia_ep_lp_all_sem_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)
```